---
title: "Data Product project"
output: html_document
date: "2023-05-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project description

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Introduction

In this project will be shown the bests beaches to surf in my city - Florianópolis - Brazil. 
This city is an island with 45 beaches. 

## Libraries

```{r}
library(leaflet)
library(dplyr)
```

## Adding the best beaches to surf - Morro das Pedras, Matadeiro, Praia Mole, Joaquina e Moçambique

```{r}
df <- leaflet(width = "100%") %>% addTiles() %>%
  addMarkers(lat = -27,722421, lng = -48.504293, popup = "Morro das Pedras") %>%
  addMarkers(lat = -27.753168, lng = -48.499642, popup = "Matadeiro") %>%
  addMarkers(lat = -27.628128, lng = -48.447781, popup = "Joaquina") %>%
  addMarkers(lat = -27.546695, lng = -48.427334, popup = "Moçambique") %>%
  addMarkers(lat = -27.602548, lng = -48.433664, popup = "Praia Mole")
(df)
```

